Bee visitation, pollination services, and plant yield in commodity and hybrid seed canola

### 2022-08-03 Manuscript/main.tex
Added tables of coefficients

Structural equation models do not have paths between all variables, which may bias the model results if this independence assumption is incorrect; this requires testing a ``basis set" of independence claims using Shipley's d-separation criteria \citep{shipley2000, shipley2009}.
The initial commodity canola pSEM was misspecfied, as several missing paths were identified (Fisher's C = 167.5, df = 64, p$<<$0.001), but the updated pSEM was deemed adequate (C = 81.6, df = 86, p = 0.62).
Similarly, the initial seed field pSEM also had several missing paths (C = 105.6, df = 76, p = 0.01), which were added, making the updated pSEM adequate (C = 72.2, k = 72, p = 0.47).
Basis sets were generated using the \texttt{dagitty} library in R 4.2.1.

@@

All component GLMMs of the pSEM were written in Stan 2.18.1 \citep{gelman2015} and run using \texttt{rstan} 2.26.13.
We used weakly informative normal priors ($\mu=0, \sigma=5$) for fixed effects and gamma priors ($\alpha=1, \beta=1$) for the variance components.
Four separate chains were run with an adaptive phase of 1000 iterations, and a sampling phase of 1000 iterations, then checked for convergence of the chains ($\hat{R} \approx$1) and low autocorrelation within chains (high $N_{eff}$).
We assessed the underlying probability distribution functions of each model using posterior predictive checks \citep{gelman2013}, and found that the probability distributions were properly specified (p$\sim$0.5).
p-values listed below (also in Tables S3 and S4) are \textit{posterior} p-values, representing the proportion of the posterior distribution that overlapped zero, with Z-scores (mean/standard deviation of posterior) showing the effect size.
% This means that while the average seed counts (per plant) were unbiased, the variance within a plant was not. 
% However, the negative binomial distribution had the closest posterior predictive checks of any other distribution. 
% Predictions from models are median values of the posterior, representing the median prediction, while intervals displayed in figures are credible intervals (CIs), representing 95\% of the samples drawn from the posterior distribution (analogous to confidence intervals, see \citealt{gelman2013}).

@@

\clearpage %Supplemental material
\include{extra_supplemental}
\include{visitors_supplemental}
\include{models_supplemental}

>>>>

Structural equation models do not have paths between all variables, which may bias the model results if this independence assumption is incorrect; this requires testing a ``basis set" of independence claims using Shipley's d-separation criteria \citep{shipley2000, shipley2009}.
The initial commodity canola pSEM was misspecfied, as several missing paths were identified (Fisher's C = 167.5, df = 64, p$<<$0.001), but the updated pSEM was deemed adequate (C = 52.0, df = 48, p = 0.32).
Similarly, the initial seed field pSEM also had several missing paths (C = 105.6, df = 76, p = 0.01), which were added, making the updated pSEM adequate (C = 72.2, k = 72, p = 0.47).
Basis sets were generated using the \texttt{dagitty} library in R 4.2.1.

@@

All component GLMMs of the pSEM were written in Stan 2.18.1 \citep{gelman2015} and run using \texttt{rstan} 2.26.13.
We used weakly informative normal priors ($\mu=0, \sigma=5$) for fixed effects and gamma priors ($\alpha=1, \beta=1$) for the variance components.
Four separate chains were run with an adaptive phase of 1000 iterations, and a sampling phase of 1000 iterations, then checked for convergence of the chains ($\hat{R} \approx$1) and low autocorrelation within chains (high $N_{eff}$).
We assessed the underlying probability distribution functions of each model using posterior predictive checks \citep{gelman2013}, and found that the probability distributions were properly specified (p$\sim$0.5).
p-values were calculated using the Z-scores (mean/SD) of the sampled posterior distributions; unless otherwise specified, p-values are lower than 0.05 (see Table \ref{tab:commCoef} and \ref{tab:seedCoef} for more detailed model summaries). 
% This means that while the average seed counts (per plant) were unbiased, the variance within a plant was not. 
% However, the negative binomial distribution had the closest posterior predictive checks of any other distribution. 
% Predictions from models are median values of the posterior, representing the median prediction, while intervals displayed in figures are credible intervals (CIs), representing 95\% of the samples drawn from the posterior distribution (analogous to confidence intervals, see \citealt{gelman2013}).

@@

\clearpage %Supplemental material
\include{extra_supplemental}
% \include{visitors_supplemental}
% \include{models_supplemental}
